$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-06 paper/paper.tex
Mention work by Ferreira

    \item
    Case $\constr{struct}$: we apply subject congruence (\autoref{thm:subject-congruence}) and proceed inductively.
  \end{itemize}
\end{proof}

@@

>>>>

    \item
    Case $\constr{struct}$: we apply subject congruence (\autoref{thm:subject-congruence}) and proceed inductively. \qedhere
  \end{itemize}
\end{proof}

@@

Castro et al. provide tooling for locally-nameless representations of process calculi in Coq \cite{Castro2020} --- where de Bruijn indices are not as popular as dependent patter matching is not as straightforward to handle.
As an example use-case, they use their tool to help automate proofs of subject reduction for a type system with session types.
